More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-07-25 2016-Weak-FH-Bisim/WeakBisim.tex
intro semantics

\section{Operational Semantics for Open pNets}
\label{section:op-semantics}

>>>>

\section{Semantics of Open pNets}
\label{section:op-semantics}

This section defines the semantics of an open \pNet as a translation into an open automaton. 
In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition. The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the 
This allows us to derive a bismulation theory for open \pNet s. As \pNet s are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.
